id & INT(10) & PK \tabularnewline\hline 







  state & TINYINT(1) & no description \tabularnewline\hline


  created & DATETIME & Fecha de creación \tabularnewline\hline
  created\_by & INT(10) & FK - creado por \tabularnewline\hline

  modified & DATETIME & no description \tabularnewline\hline
  modified\_by & INT(10) & no description \tabularnewline\hline


  version & int(10) & no description \tabularnewline\hline

  ordering & INT(11) & no description \tabularnewline\hline








%each field
	id\_organo & INT(10) & \'Organo: \tabularnewline\hline 
	anoj & YEAR(4) & A\~no j.:A\~no judicial \tabularnewline\hline 
	id\_secretaria & INT(10) & Secretar\'i{}a: \tabularnewline\hline 
	fh\_recepcion & DATETIME & FECHA Y HORA DE RECEPCI\'ON: \tabularnewline\hline 
	field3 & VARCHAR(45) & DOMICILIO DONDE SE GENERA LA VIOLENCIA: \tabularnewline\hline 
	field4 & INT(10) & DELEGACION: \tabularnewline\hline 
	field10 & TINYINT(1) & Art. 66 Frac. I: \tabularnewline\hline 
	field11 & TINYINT(1) & Art. 66 Frac. II: \tabularnewline\hline 
	field12 & TINYINT(1) & Art. 66 Frac. III: \tabularnewline\hline 
	field13 & TINYINT(1) & Art. 66 Frac. IV: \tabularnewline\hline 
	field14 & TINYINT(1) & Art. 66 Frac. V: \tabularnewline\hline 
	field15 & TINYINT(1) & Art. 71 Frac. I: \tabularnewline\hline 
	field16 & TINYINT(1) & Art. 71 Frac. II: \tabularnewline\hline 
	field17 & TINYINT(1) & Art. 71 Frac. III: \tabularnewline\hline 
	field18 & TINYINT(1) & Art. 71 Frac. IV: \tabularnewline\hline 
	organo1 & INT(10) & JUZGADO EN TURNO: \tabularnewline\hline 
	field8 & VARCHAR(45) & RESOLUCI\'ON: \tabularnewline\hline 
	field9\_isMoral & TINYINT(1) & NOMBRE QUIEN INFORMO RESOLUCI\'ON (isMoral): \tabularnewline\hline 
	field9\_paterno & VARCHAR(255) & NOMBRE QUIEN INFORMO RESOLUCI\'ON (paterno): \tabularnewline\hline 
	field9\_materno & VARCHAR(45) & NOMBRE QUIEN INFORMO RESOLUCI\'ON (materno): \tabularnewline\hline 
	field9\_nombre & VARCHAR(45) & NOMBRE QUIEN INFORMO RESOLUCI\'ON (nombre): \tabularnewline\hline 
